Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-02-18 analysis/paper/paper.qmd

@@

In Jonathon Swift's classic satirical novel *Gulliver's Travels* (1726) Gulliver visits the fictional Grand Academy of Lagado in Balnibarbi, a caricature of the Royal Society of London, and meets several researchers working on wildly impractical projects, including one attempting to extracting sunbeams out of cucumbers.

>>>>

In the classic satirical novel *Gulliver's Travels* (1726) by Irish writer Jonathon Swift Gulliver visits the fictional Grand Academy of Lagado in Balnibarbi, a caricature of the Royal Society of London, and meets several researchers working on wildly impractical projects, including one attempting to extracting sunbeams out of cucumbers. This is usually interpreted as a subversive and anti-colonial parody depicting institutionalized research as an absurd fund-raising activity with no practical benefits to society [@alff2014swift; @nicolson1937scientific]. @feinbergExtractingSunbeamsCucumbers2011

@@
